
---
title: 'business sharks Lukas and Julien '
author: "Lukas and Julien"
date: "2025-11-03"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
---

```{r,echo=FALSE, message=FALSE, warning=FALSE}
options(repos = c(CRAN = "https://cloud.r-project.org/"))
if (!require(ggplot2)) install.packages("ggplot2")  
if (!require(mlogit)) install.packages("mlogit")
if (!require(ggplot2)) install.packages("ggplot2")
if (!require(reshape2)) install.packages("reshape2")
if (!require(dplyr)) install.packages("dplyr")
if (!require(tidyr)) install.packages("tidyr")
if (!require(readxl)) install.packages("readxl")
install.packages("lubridate")
install.packages("readr")
install.packages("ggplot2")
install.packages("MASS")
install.packages("maps")



# Loading libraries
library(maps)

library(mlogit)
library(ggplot2)
library(reshape2)
library(dplyr)
library(tidyr)
library(readxl)
library(lubridate)
library(readr)
library(dplyr)
library(ggplot2)
library(magrittr)

```

#Introduction

This study focuses on the excess returns generated by American politicians’ stock trades. The main objective is to analyze the relationship between excess returns and net gains across political party, state, and individual politicians.



1)  Organization of the data 

```{r, echo=FALSE}
df <- read.csv("project.csv", stringsAsFactors = FALSE)
names(df)
```
```{r, echo=FALSE, results='hide'}
data <- read.csv("project.csv")
head(df)
```

The dataset consists of 17 columns, as presented above. However, the raw data required reorganization and cleaning before analysis.

After preprocessing, several unnecessary columns were removed and missing column names were eliminated. Date variables were standardized across all observations. Trade size values reported as ranges were converted into minimum and maximum values, and a midpoint measure was constructed.

Additional variables were created, including:

Trade delay, measured in days between the trade date and filing date

Net trade direction, where purchases were coded as +1 and sales as −1

Midpoint trade size, representing the average of the reported range

Net gain, calculated as excess return multiplied by trade direction

```{r,echo=FALSE, message=FALSE, warning=FALSE}

#change of the data

# delete some inutile column and inutile line

df$Quiver_Upload_Time <- NULL
df$Status <- NULL

bad <- which(is.na(names(df)) | names(df) == "")

df <- df[, !(is.na(names(df)) | names(df) == ""), drop = FALSE]

## cleaning data all across all column by converting dates to numbers :

# creation of a function 
coerce_date <- function(x) {
  x <- trimws(as.character(x))
  out <- suppressWarnings(ymd(x))
  if (all(is.na(out))) out <- suppressWarnings(dmy(x))
  if (all(is.na(out))) out <- suppressWarnings(mdy(x))
  if (all(is.na(out))) out <- suppressWarnings(readr::parse_date(x,
                      locale = locale(date_names = "en")))
  as.Date(out)
}

# application of the function 
library(dplyr)
library("lubridate")

df <- df %>% mutate(
    Traded        = coerce_date(Traded),
    Filed         = coerce_date(Filed),
    last_modified = coerce_date(last_modified)) # write_csv(df, "project_clean.csv")

## Converting trade size usd into intervall

# Robust function to handle vectors properly
parse_min_max <- function(x) {
  # If x is NA or empty (works for vectors of length 1)
  if (length(x) != 1 || is.na(x) || trimws(x) == "") return(c(min = NA, max = NA))
  
  # Remove $ and commas
  x_clean <- gsub("[$,]", "", as.character(x))
  
  # Extract all numbers (integer or decimal)
  nums <- as.numeric(unlist(regmatches(x_clean, gregexpr("[0-9]+\\.?[0-9]*", x_clean))))
  
  # If no numbers found
  if (length(nums) == 0) return(c(min = NA, max = NA))
  
  # Return min and max
  c(min = min(nums, na.rm = TRUE), max = max(nums, na.rm = TRUE))
}

# Apply to the entire column safely
parsed <- t(sapply(as.character(df$Trade_Size_USD), parse_min_max))
parsed <- as.data.frame(parsed)

# Add min and max columns to your dataframe
df$Trade_Size_USD_min <- parsed$min
df$Trade_Size_USD_max <- parsed$max

## delete tickertype
df <- df[, -2]

## Creating Trade Delay (in days)

df <- df %>%
  mutate(
    trade_delay = as.numeric(Filed - Traded)
  )


## Creating Net Trade Direction

df <- df %>%
  mutate(
    net_trade_direction = case_when(
      Transaction == "Purchase"           ~ 1,
      Transaction %in% c("Sale", "Sale (Partial)", "Sale (Full)") ~ -1,
      Transaction == "Exchange"           ~ 0,   # or NA_real_ if you prefer
      TRUE                                     ~ NA_real_
    )
  )


total_direction <- sum(df$net_trade_direction, na.rm = TRUE)


## Creating Midpoint for Trade Size

df <- df %>%
  mutate(
    trade_size_mid = (Trade_Size_USD_min + Trade_Size_USD_max)/2
  )
## calculate the net gain/lost

df$net_gain <- df$excess_return * df$net_trade_direction
names(df)

```

After reorganization, the dataset now contains 21 columns. Three original variables were removed and seven new variables were added. The most important constructed variables are net gain, midpoint trade size, and trade delay. Net gain reflects the economic outcome of each transaction by combining excess return with trade direction.


2) Trade Size and number


We examine both the size and the number of trades on a yearly and monthly basis and compute correlations between these measures.

```{r,,echo=FALSE}
years  <- format(df$Filed, "%Y") 
month <- format(df$Filed, "%Y-%m")   

stpymid <- tapply(df$trade_size_mid, years, sum)
stpymax<-tapply(df$Trade_Size_USD_max, years, sum)
stpymin <- tapply(df$Trade_Size_USD_min, years, sum)

stpymmid<- tapply(df$trade_size_mid, month, sum)
stpymmax<-tapply(df$Trade_Size_USD_max, month, sum)
stpymmin<- tapply(df$Trade_Size_USD_min, month, sum)

##number of trade per year/per month

Ntpy <- table(years)#give the number for each year
Ntpm <- table(month)# give the number for each month


```

The mid size of trades per year is presented as follows: 
```{r,,echo=FALSE}
stpymid
```
While the number of trades per year is: 
```{r,,echo=FALSE}
Ntpy
```
To assess whether a relationship exists between monthly trade volume and the number of transactions, both variables are plotted over time:

```{r,echo=FALSE, message=FALSE, warning=FALSE}

library(ggplot2)

# plot of the trade size
dates <- as.Date(paste0(names(stpymmin), "-01"))
dates_year <- as.Date(paste0(names(stpymin), "-01-01"))
plot(dates, stpymmin,
     type = "l",
     xlab = "Date",
     ylab = "Trade Size Mid (Sum)",
     main = "Monthly Trade Size (Mid)",
     col = "blue",
     lwd = 2)
     

# plot of number of trade

dates2 <- as.Date(paste0(names(Ntpm), "-01"))

plot(dates2, Ntpm,
     type = "l",
     xlab = "Date",
     ylab = "Number of trade",
     main = "Monthly number of trade",
     col = "blue",
     lwd = 2)
```

The plot raises some uncertainty about the relationship. Based on the analysis, the Spearman correlation between the number of trades per month and trade size per month is `r cor(Ntpm, stpymmid, method="spearman")` and the Pearson correlation is `r cor(Ntpm, stpymmid, method = "pearson")`, indicating a strong positive association.

Overall, there is a strong correlation between monthly trade size and the number of trades. This is intuitive, as months with more transactions tend to exhibit higher total traded values. This relationship is further illustrated using a linear trend plot.

```{r,echo=FALSE,message=FALSE, warning=FALSE}

library(ggplot2)
df_plot <- data.frame(
  num_trades = as.numeric(Ntpm),
  trade_size = as.numeric(stpymmid)
)

ggplot(df_plot, aes(x = num_trades, y = trade_size)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Trade Size vs Number of Trades",
       x = "Number of Trades",
       y = "Trade Size") +
  theme_minimal()

```

Next, we test whether the number of trades varies systematically across months or years.

```{r, echo = FALSE}
months <- as.numeric(substr(names(Ntpm), 6, 7))
year <- as.numeric(substr(names(Ntpy),1,4))
```

The Spearman correlation per year is `r cor(year, as.numeric(Ntpy), method = "spearman")` and per month is `r cor(months, as.numeric(Ntpm), method = "spearman")`, indicating no meaningful correlation.

The Spearman correlation between the number of trades and year, as well as between the number of trades and month, is close to zero. This indicates that trading activity does not exhibit significant seasonal or long-term time trends.

```{r,echo=FALSE,message=FALSE, warning=FALSE}

library(ggplot2)

df_plot <- data.frame(
  month = months,
  num_trades = as.numeric(Ntpm)
)

ggplot(df_plot, aes(x = month, y = num_trades)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE, color = "red") +
  scale_x_continuous(breaks = 1:12, labels = month.abb) +
  labs(x = "Month", y = "Number of Trades", title = "Number of Trades vs Month") +
  theme_minimal()

```
The corresponding plot confirms that the number of trades remains relatively stable across months.
We can also compute the same for the trade size. The average trade size is `r mean(c(mean(df$Trade_Size_USD_min,na.rm = TRUE), mean(df$Trade_Size_USD_max,na.rm = TRUE)))`


3) Chamber, party and excess return

 3.1) Correlation and dominant party

We now analyze whether excess returns differ by political chamber or party.

```{r,echo=FALSE,message=FALSE, warning=FALSE}

#Excess return ↔ Chamber correlation

#translate the binary variable into 0/1 and compute the Pearson correlation coefficient

Chamber1 <- ifelse(df$Chamber == "House", 1, 0)
Party1 <-  ifelse(df$Party == "R", 1, 0)

```

The correlation between Chamber and excess return is `r cor(Chamber1, df$excess_return, use = "complete.obs", method = "pearson")`, and between Chamber and net gain is
`r cor(Chamber1, df$net_gain, use = "complete.obs", method = "pearson")`.

For Party, the correlations are `r cor(Party1, df$excess_return, use = "complete.obs", method = "pearson")` and
`r cor(Party1, df$net_gain, use = "complete.obs", method = "pearson")`.

These results indicate very weak relationships between political chamber and excess return, as well as between party affiliation and excess return. Therefore, neither chamber nor party appears to be strongly associated with trading performance.

Next, trades are grouped by party and chamber within each state. The results are presented below.

```{r, echo = FALSE}

state_chamber_party <- df %>%
  group_by(State, Chamber, Party) %>%
  summarise(Num_Trades = n(), .groups = 'drop') %>%
  arrange(State, Chamber, desc(Num_Trades))

head(state_chamber_party)

```

Let us now examine the distribution of party affiliation across states.

```{r, echo = FALSE}

##Count trades by State × Chamber × Party

#Summarize counts
state_chamber_party <- df %>%
  group_by(State, Chamber, Party) %>%
  summarise(Num_Trades = n(), .groups = 'drop') %>%
  arrange(State, Chamber, desc(Num_Trades))

head(state_chamber_party)


#If we want to see party dominance as percentages within each state/chamber:

state_chamber_party <- state_chamber_party %>%
  group_by(State, Chamber) %>%
  mutate(Total_Trades = sum(Num_Trades),
         Party_Percent = Num_Trades / Total_Trades * 100)
         
##Visualize with a stacked bar ggplot(state_chamber_party, aes(x = State, y = Party_Percent, fill = Party)) +

ggplot(data = state_chamber_party, aes(x = State, y = Party_Percent, fill = Party)) +
  geom_col() +
  facet_wrap(~ Chamber) +
  labs(
    y = "Percentage of Trades",
    title = "Party Distribution by State and Chamber"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
Next, we identify the dominant political party within each state and chamber using both heatmaps and geographic maps.

```{r, echo = FALSE,message=FALSE, warning=FALSE }
##Dominant Party
library(dplyr)
library(ggplot2)
library(maps)

dominant_party <- state_chamber_party %>%
  group_by(State, Chamber) %>%
  slice_max(order_by = Num_Trades, n = 1) %>%
  select(State, Chamber, Party, Num_Trades)

dominant_party

print(dominant_party, n = Inf)


##Creating a Heatmap

## Heatmap for dominant party in each state by house and senate

# Determine dominant party per State/Chamber (without the percentage, just the party that dominates)
dominant_party <- state_chamber_party %>%
  group_by(State, Chamber) %>%
  slice_max(order_by = Num_Trades, n = 1) %>%
  ungroup()
  
#Creating heatmap

ggplot(dominant_party, aes(x = State, y = Chamber, fill = Party)) +
  geom_tile(color = "white") +
  scale_fill_manual(values = c("D" = "blue", "R" = "red")) +
  labs(title = "Dominant Party by State and Chamber",
       x = "State",
       y = "Chamber") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
#Creating a map 

dominant_party <- dominant_party %>%
  mutate(region = tolower(State)) 
  
us_states <- map_data("state")

map_data_party <- us_states %>%
  left_join(dominant_party, by = "region")

  
ggplot(map_data_party, aes(x = long, y = lat, group = group, fill = Party)) +
  geom_polygon(color = "black") +
  coord_fixed(1.3) +
  facet_wrap(~ Chamber) +
  scale_fill_manual(values = c("D" = "blue", "R" = "red", "I" = "green")) +
  labs(title = "Dominant Party by State and Chamber") +
  theme_void() +
  theme(legend.position = "bottom")
```

We now examine the intensity of party dominance across states.

```{r, echo = FALSE ,message=FALSE, warning=FALSE }
library(ggplot2)
library(maps)

##Heatmap (intensity)
# Create a signed percent: Democrat = positive, Republican = negative
state_chamber_party <- state_chamber_party %>%
  mutate(Party_Signed_Percent = ifelse(Party == "D", Party_Percent, -Party_Percent))

#Creating Heatmap
ggplot(state_chamber_party, aes(x = State, y = Chamber, fill = Party_Signed_Percent)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(
    low = "red",       # Republican
    mid = "white",     # neutral
    high = "blue",     # Democrat
    midpoint = 0,
    limits = c(-100, 100),
    name = "% of Trades\n(Red=R, Blue=D)"
  ) +
  labs(title = "Party Dominance Heatmap by State and Chamber",
       x = "State",
       y = "Chamber") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#map
state_chamber_party <- state_chamber_party %>%
  mutate(region = tolower(State))
  
us_states <- map_data("state")  
map_data_party <- us_states %>%
  left_join(state_chamber_party, by = "region")

ggplot(map_data_party, aes(x = long, y = lat, group = group, fill = Party_Signed_Percent)) +
  geom_polygon(color = "black") +
  coord_fixed(1.3) +
  facet_wrap(~ Chamber) +   # separate House and Senate
  scale_fill_gradient2(
    low = "red",       # Republican
    mid = "white",     # neutral
    high = "blue",     # Democrat
    midpoint = 0,
    limits = c(-100, 100),
    name = "% of Trades\n(Red=R, Blue=D)"
  ) +
  labs(title = "Party Dominance by State and Chamber") +
  theme_void() +
  theme(legend.position = "bottom")
  

```


  3.2) Excess return by Party

```{r, echo = FALSE}
df %>%
  group_by(Party) %>%
  summarise(
    Mean_Excess_Return = mean(excess_return, na.rm = TRUE),
    Median_Excess_Return = median(excess_return, na.rm = TRUE),
    SD_Excess_Return = sd(excess_return, na.rm = TRUE),
    Num_Trades = n()
  )



```

We now examine the statistical properties of excess returns.

```{r}
summary(df$excess_return)
```
The initial summary appears highly negative, which is primarily due to the presence of missing values. After excluding missing observations, the corrected statistics are as follows:

The mean excess return is: `r mean(df$excess_return, na.rm = TRUE)    # mean ignoring NAs`
The median excess return is:   `r median(df$excess_return, na.rm = TRUE)  # median ignoring NAs`
The standard deviation is: `r sd(df$excess_return, na.rm = TRUE)      # standard deviation ignoring NAs`

Interpretation

On average, trades underperformed the market benchmark by approximately 15%.

The mean is slightly higher than the median because a small number of large positive outcomes increase the average.

More than half of all trades underperformed the benchmark by roughly 28%, confirming a negatively skewed distribution.

The very high standard deviation indicates substantial volatility in trade outcomes, with extreme outliers such as 10,885 and −318 strongly influencing dispersion.

Distribution of excess returns - Histogram

```{r, echo = FALSE,message=FALSE, warning=FALSE  }

library(ggplot2)
# Histogram limited to a reasonable range to visualize most trades
ggplot(df, aes(x = excess_return)) +
  geom_histogram(bins = 100, fill = "steelblue", color = "white") +
  xlim(-500, 500) +  # limits extreme outliers
  labs(title = "Distribution of Excess Return (Limited View)",
       x = "Excess Return",
       y = "Count") +
  theme_minimal()
```

The histogram suggests an approximately normal distribution with a pronounced right tail, indicating positive skewness driven by extreme high returns.

A negative value of net_gain represents a loss, while a positive value represents a gain.
The top ten overperforming trades with highest returns based on net gain, are shown below.

```{r, echo = FALSE}
df %>%
  filter(!is.na(net_gain)) %>%
  arrange(desc(net_gain)) %>%
  select(Name, Party, Company, Ticker, net_gain) %>%
  head(10)  # top 10 highest excess returns

```

```{r}
#number of trades per ticker  

ntpt <- df %>% group_by(Ticker) %>%  summarise(Num_Trades = n())
ntpt

max <-ntpt$Ticker[ntpt$Num_Trades == max(ntpt$Num_Trades)]

```


The most frequently traded ticker is `r max`.

Individual-level aggregation:

Trades were aggregated by individual politician to compute total activity and outcomes.

```{r, echo = FALSE}
df_person <- df %>%
  group_by(Name, Party, State, Chamber ) %>%
  summarise(
    total_trades = n(),
    total_trade_value = sum(trade_size_mid, na.rm = TRUE),
    tot_excess_return  = sum(excess_return, na.rm = TRUE),
    Number_of_sale     = sum(Transaction == "Sale", na.rm = TRUE),
    Number_of_purchase = sum(Transaction == "Purchase", na.rm = TRUE),
    Net_gain =sum(net_gain, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(total_trades))

df_person

```

3.3) Time and performance

We test whether excess return is related to the timing of trades.

```{r, echo =FALSE}
df$Trade_Date_Num <- as.numeric(df$Traded)  # convert Date to numeric
correlation <- cor(df$Trade_Date_Num , df$excess_return, use = "complete.obs")
correlation
```

The correlation is close to zero, indicating no direct relationship between trade date and excess return.

We further explore monthly and yearly patterns.

```{r, echo = FALSE }



plot(df$Traded, df$net_gain,
     xlab = "Trade Date",
     ylab = "net gain",
     main = "Net gain vs Trade Date")
abline(lm(excess_return ~ as.numeric(Traded), data=df), col="red")


```

What is the relation between net gain and month? 

```{r, echo= FALSE}
df_monthly <- df %>%
  mutate(Month = as.Date(paste0(format(Traded, "%Y-%m"), "-01"))) %>%  # first day of month
  group_by(Month) %>%
  summarise(
    avg_excess = mean(net_gain, na.rm = TRUE),
    sd_excess = sd(net_gain, na.rm = TRUE),
    n_trades = n()
  ) %>%
  arrange(Month)

plot(df_monthly$Month, df_monthly$avg_excess, type="b",
     xaxt = "n",  # suppress default x-axis
     xlab = "Month", ylab = "Net gain",
     main = "Net gain per Month")

# Add formatted month labels
axis(1, at = df_monthly$Month, labels = format(df_monthly$Month, "%b %Y"), las=2)
```

The average net gain shows a gradual increase over time but remains close to zero. Early years, particularly 2012, contain limited observations and should be interpreted with caution.
     

relation beetween excess of return and month 

```{r, echo = FALSE}



df_yearly <- df %>%
  mutate(Year = as.Date(paste0(format(Traded, "%Y"), "-01-01"))) %>%  # first year
  group_by(Year) %>%
  summarise(
    avg_excess = mean(net_gain, na.rm = TRUE),
    sd_excess = sd(net_gain, na.rm = TRUE),
    Nm=sum(net_gain, na.rm = TRUE),
    n_trades = n()
  ) %>%
  arrange(Year)

plot(df_yearly$Year, df_yearly$avg_excess, type="b",
     xlab="Year", ylab="Average Excess Return",
     main="Average Excess Return per Year")
     
    
plot(df_yearly$Year, df_yearly$Nm, type="b",
     xlab="Year", ylab="sum of return",
     main="sum of excees return per Year")
     
    
plot(df_yearly$Year, df_yearly$n_trades, type="b",
     xlab="Year", ylab="number of transaction",
     main="number of transaction per Year")    

```

The average excess return increases over time. To avoid distortion from the low-activity year 2012, this year is excluded from further correlation analysis.

```{r}
plot(df_yearly$n_trades, df_yearly$avg_excess)
```
The point corresponding to 2012 biases the relationship.

The correlation is as follows:
``` {r, echo = FALSE}
df_filtered <- df_yearly[df_yearly$Year >= as.Date("2013-01-01"), ]

correlation1 <- cor(
  df_filtered$n_trades,
  df_filtered$avg_excess,
  use = "complete.obs"
)
correlation1

```
A modest positive relationship is observed between the number of trades and average net gain.
```{r}
plot(df_filtered$n_trades, df_filtered$avg_excess)

```


  3.4) excess return, trade size by party 
  
##1. Histogram of trade size

We begin by examining the distribution of trade size. Because trade sizes are highly skewed, we visualize the distribution on a logarithmic scale.

#LOG scale

```{r}
ggplot(df, aes(x = trade_size_mid)) +
  geom_histogram(bins = 50, fill = "steelblue", color = "white") +
  scale_x_log10(labels = scales::comma) +
  labs(
    title = "Distribution of Trade Size (Log Scale)",
    x = "Trade Size (USD, log10)",
    y = "Count"
  ) +
  theme_minimal()
```

To improve interpretability, we also group trades into size categories.

```{r}
#categorising trade size

df <- df %>%
  mutate(trade_size_cat = case_when(
    trade_size_mid < 1e4  ~ "< $10k",
    trade_size_mid < 5e4  ~ "$10k–$50k",
    trade_size_mid < 1e5  ~ "$50k–$100k",
    trade_size_mid < 5e5  ~ "$100k–$500k",
    TRUE                  ~ "> $500k"
  ))

ggplot(df, aes(x = trade_size_cat)) +
  geom_bar(fill = "steelblue") +
  labs(
    title = "Trade Size Categories",
    x = "Trade Size Category",
    y = "Number of Trades"
  ) +
  theme_minimal()
```

##2. Boxplot: excess return by party

We next compare the distribution of excess returns across political parties.

```{r}
ggplot(df, aes(x = Party, y = excess_return)) +
  geom_boxplot(outlier.alpha = 0.3) +
  coord_cartesian(ylim = c(-300, 300)) +
  labs(
    title = "Excess Return by Party",
    x = "Party",
    y = "Excess Return"
  ) +
  theme_minimal()
```

##3.1 Boxplot: excess return by chamber

We also examine whether excess returns differ between the House and the Senate.

```{r}
ggplot(df, aes(x = Chamber, y = excess_return)) +
  geom_boxplot(outlier.alpha = 0.3) +
  coord_cartesian(ylim = c(-300, 300)) +
  labs(
    title = "Excess Return by Chamber",
    x = "Chamber",
    y = "Excess Return"
  ) +
  theme_minimal()
```

##3.2 excess return by state/ net gain by state 

To explore geographic variation, we compare excess return distributions across states and compute state-level averages for both excess return and net gain.

```{r}
ggplot(df, aes(x = State, y = excess_return)) +
  geom_boxplot(outlier.alpha = 0.3) +
  coord_cartesian(ylim = c(-300, 300)) +
  labs(
    title = "Excess Return by State",
    x = "State",
    y = "Excess Return"
  ) +
  theme_minimal() 
  
state_means <- df %>%
  group_by(State) %>%
  summarise(mean_excess_return = mean(excess_return, na.rm = TRUE))

state_means2 <- df %>%
  group_by(State) %>%
  summarise(net_gain = mean(net_gain, na.rm = TRUE))


us_states <- map_data("state")  
  
state_means <- state_means %>%
  mutate(State = tolower(State))  
  
state_means2 <- state_means2 %>%
  mutate(State = tolower(State))  

map_df <- left_join(
  us_states,
  state_means,
  by = c("region" = "State")
)
  
ggplot(map_df, aes(x = long, y = lat, group = group, fill = mean_excess_return)) +
  geom_polygon(color = "white", linewidth = 0.2) +
  coord_fixed(1.3) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    na.value = "grey90"
  ) +
  labs(
    title = "Mean Excess Return by State",
    fill = "Mean Excess Return"
  ) +
  theme_void()
  
  
map_df2 <- left_join(
  us_states,
  state_means2,
  by = c("region" = "State")
)
  
ggplot(map_df2, aes(x = long, y = lat, group = group, fill = net_gain)) +
  geom_polygon(color = "white", linewidth = 0.2) +
  coord_fixed(1.3) +
  scale_fill_gradient2(
    low = "blue",
    mid = "white",
    high = "red",
    midpoint = 0,
    na.value = "grey90"
  ) +
  labs(
    title = "net gain by state",
    fill = "Mean net gain"
  ) +
  theme_void()
```

##3.3 Boxplot: excess return by party

To visualize the dispersion and individual observations simultaneously, we overlay points on the party-level boxplots.
```{r}
ggplot(df, aes(x = Party, y = excess_return)) +   geom_point(na.rm = TRUE)+
  geom_boxplot(outlier.alpha = 0.3) +
  coord_cartesian(ylim = c(-300, 300)) +
  labs(
    title = "Excess Return by Party",
    x = "Party",
    y = "Excess Return"
  ) +
  theme_minimal()   
```
##4. Boxplot: excess return by transaction type

We further compare excess returns across transaction types (e.g., purchases and sales).

```{r}
ggplot(df, aes(x = Transaction, y = excess_return)) +
  geom_boxplot(outlier.alpha = 0.3) +
  coord_cartesian(ylim = c(-300, 300)) +
  labs(
    title = "Excess Return by Transaction Type",
    x = "Transaction Type",
    y = "Excess Return"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

##6. Clean time series: number of trades over time

Finally, we construct a monthly time series of the number of trades to illustrate how trading activity evolves over time.

```{r}
df_ts <- df %>%
  mutate(Month = as.Date(paste0(format(Traded, "%Y-%m"), "-01"))) %>%
  group_by(Month) %>%
  summarise(num_trades = n(), .groups = "drop")

ggplot(df_ts, aes(x = Month, y = num_trades)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Number of Trades Over Time (Monthly)",
    x = "Month",
    y = "Number of Trades"
  ) +
  theme_minimal()
```

Correlation between trade size and party

We test whether total traded value differs between parties using a two-sample t-test.

```{r}
df_two <- df_person |> filter(Party %in% c("R", "D"))

t.test(total_trade_value ~ Party, data = df_two)
```

The test suggests no statistically significant difference between the two parties; trade values appear broadly balanced.

  3.5) Sales and purchases
  
We summarise total traded value by transaction type and report the number of sales, purchases, and exchanges.

```{r}
df_sale <- df %>%
  group_by(Transaction)%>%
  summarise(Trade_size = sum(trade_size_mid))
View(df_sale)

sum(data$Transaction == "Sale" | data$Transaction == "Sale (Full)" | data$Transaction == "Sale (Partial)", na.rm = TRUE )
sum(data$Transaction == "Purchase", na.rm = TRUE)
sum(data$Transaction == "Exchange", na.rm = TRUE)
```
   
A correlation comparison between sales and purchases is not meaningful because the number of observations differs substantially between these transaction types.


#Conclusion

This studies show a strong evidence of no correlation beetween excees return and party/ Chamber. Even if we get a big dataset, this was not well spread and it has also biased some result and it was not preccise for the most important thing : We did'nt know the pair between sell and purchase. Based on our data we have been able to change way and to analyzed Party and Chamber dominace and state  and correlation between number of sale and size of it. We decided to transform excess return to get net gain. 

In conclusion this was not precise but we can say that the trade depend not on politician party but on each person. Because of lack of information we couldn't studies the impact of region on excees return.





#use of AI 

The use of AI was very necessary to fix many technical problem. It has been used for exemple to fix problem of Knit with the use of latex_engine: xelatex. 
What is more a lot of function has been found in R to manage so code, such as lubridate and map. Many code have been thinking by AI but it as always been modify or at least been understand apart from some part to delete and reorganized data. 
The AI was a tool to code, but not to give idea for which one to use.  
Rmarkdown was made by our own without AI because of the facility to compute it. 